Type-safe client-server communication for functional web applications

### 2014-03-01 paper.tex
Fix some metadata.
Add note about simplification and error handling to implementation section.

\conferenceinfo{ICFP '14}{Month d--d, 20yy, City, ST, Country} 
\copyrightyear{20yy} 
\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
\doi{nnnnnnn.nnnnnnn}

@@

\titlebanner{banner above paper title}        % These are ignored unless
\preprintfooter{short description of paper}   % 'preprint' option specified.

@@

\begin{code}
import Data.List (find)
import Haste.App
import Haste.App.Concurrent
import qualified Control.Concurrent as CC

@@

\begin{code}
srvAwait :: Useless RcptList -> Server String
srvAwait uRcpts = do
  rcpts <- mkUseful uRcpts
  sid <- getSessionID
  liftIO $ do
    recipients <- CC.withMVar rcpts return
    case find ((== sid) . fst) recipients of
      Just (_, mv) -> CC.takeMVar mv
      _            -> fail "Unregistered session!"
\end{code}

@@

\section{Implementation}

@@

@@

\paragraph{The \lstinline!App! monad}
The \lstinline!App! monad is where remote functions are declared, server state
is initialized and program flow is finally handed over to the \lstinline!Client!
monad. Slightly simplified, its definition is as follows.

@@

\begin{code}
onEvent :: [(CallID, Method)] -> JSON -> IO ()
onEvent mapping msg = do
  let (nonce, identifier, args) = deserialize msg
      f = find identifier mapping
  result <- f args
  webSocketSend $ serialize (nonce, result)
\end{code}

The function corresponding to the RPC call's identifier is looked up in the
identifier-function mapping generated by the \lstinline!App! computation and
applied to the list of arguments; the return value is bundled up with the
call's nonce and sent back to the client.

>>>>

\conferenceinfo{ICFP~'14}{September 1--3, 2014, Gothenburg, Sweden} 
\copyrightyear{2014}
\copyrightdata{978-1-nnnn-nnnn-n/14/09}
\doi{nnnnnnn.nnnnnnn}

@@

\titlebanner{-- ICFP '14 draft submission --}        % These are ignored unless
\preprintfooter{-- -- -- -- draft -- -- -- --}   % 'preprint' option specified.

@@

\begin{code}
import Haste.App
import Haste.App.Concurrent
import qualified Control.Concurrent as CC

@@

\begin{code}
srvAwait :: Useless RcptList -> Server String
srvAwait uRcpts = do
  rcpts <- mkUseful uRcpts
  sid <- getSessionID
  liftIO $ do
    recipients <- CC.withMVar rcpts return
    case lookup sid recipients of
      Just mv -> CC.takeMVar mv
      _       -> fail "Unregistered session!"
\end{code}

@@

\section{Implementation}\label{sec:impl}

@@

The implementation described here is a slight simplification of our
implementation, removing some performance enhancements and error handling
clutter in the interest of clarity.

@@

\paragraph{The \lstinline!App! monad}
The \lstinline!App! monad is where remote functions are declared, server state
is initialized and program flow is finally handed over to the \lstinline!Client!
monad. Its definition is as follows.

@@

\begin{code}
onEvent :: [(CallID, Method)] -> JSON -> IO ()
onEvent mapping msg = do
  let (nonce, identifier, args) = deserialize msg
      Just f = lookup identifier mapping
  result <- f args
  webSocketSend $ serialize (nonce, result)
\end{code}

The function corresponding to the RPC call's identifier is looked up in the
identifier-function mapping generated by the \lstinline!App! computation and
applied to the list of arguments; the return value is bundled up with the
call's nonce and sent back to the client. Note that during normal operation,
it is not possible for the client to submit an RPC call with a non-existent
call identifier, hence the irrefutable pattern match on \lstinline!Just f!.
Should this pattern match fail, this is a sure sign of malicious tampering;
the resulting exception is caught and the session is dropped as it is no longer
meaningful to continue.
